### 2012-05-23 inst/examples/policycosts/L1.Rmd
use the selected coefficient to implement a comparable cost in each case

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
cache=FALSE
````

@@

``` {r simulate_policy, cache=cache}
sims <- lapply(1:100, function(i)
  simulate_optim(f, pars, x_grid, h_grid, x0, policycost$D, z_g, z_m, z_i, opt$D, profit=profit, penalty=penalty)
  )
````

@@

``` {r tidy, cache=cache}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

@@

``` {r rep1, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

@@

``` {r rep2, cache=cache}
ggplot(subset(dt,reps==2)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

@@

``` {r rep1profit, cache=cache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit_fishing)) +
  geom_line(aes(time, policy_cost), col="darkblue")

@@

``` {r policycost, cache=cache}
costs <- dt[ , sum(policy_cost), by=reps]
profits <-dt[ , sum(profit_fishing), by=reps]

@@

``` {r policy, cache=cache}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (x_grid[Var1]), col=h_grid[value]-h_grid[Var2])) + 
    labs(x = "prev harvest", y = "fishstock") +
      scale_colour_gradientn(colours = rainbow(4)) 
````

@@

``` {r harvestchanges, cache=cache}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (h_grid[value]), col = x_grid[Var1]), position=position_jitter(w=.005,h=.005), alpha=.5) + 
    labs(x = "prev harvest", y = "harvest") +
      scale_colour_gradientn(colours = rainbow(4)) 
````

>>>>

``` {r policycost_optim }
c2 <- 1.52
penalty <- L1(c2)
policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                    profit, delta, reward, penalty = penalty)
````

@@

``` {r simulate_policy}
sims <- lapply(1:100, function(i)
  simulate_optim(f, pars, x_grid, h_grid, x0, policycost$D, z_g, z_m, z_i, opt$D, profit=profit, penalty=penalty)
  )
````

@@

``` {r tidy}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

@@

``` {r rep1}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

@@

``` {r rep2}
ggplot(subset(dt,reps==2)) +
  geom_line(aes(time, alternate)) +
  geom_line(aes(time, fishstock), col="darkblue") +
  geom_line(aes(time, harvest), col="purple") + 
  geom_line(aes(time, harvest_alt), col="darkgreen") 
````

@@

``` {r rep1profit}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit_fishing)) +
  geom_line(aes(time, policy_cost), col="darkblue")

@@

``` {r policycost}
costs <- dt[ , sum(policy_cost), by=reps]
profits <-dt[ , sum(profit_fishing), by=reps]

@@

``` {r policy}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (x_grid[Var1]), col=h_grid[value]-h_grid[Var2])) + 
    labs(x = "prev harvest", y = "fishstock") +
      scale_colour_gradientn(colours = rainbow(4)) 
````

@@

``` {r harvestchanges}
policy <- sapply(1:length(h_grid), function(i) policycost$D[[i]][,1])
ggplot(melt(policy)) + 
  geom_point(aes(h_grid[Var2], (h_grid[value]), col = x_grid[Var1]), position=position_jitter(w=.005,h=.005), alpha=.5) + 
    labs(x = "prev harvest", y = "harvest") +
      scale_colour_gradientn(colours = rainbow(4)) 
````
